Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-08-06 paper/paper.tex
minor fixes

- failure of averaging
- complex interrelationships b/w parameters and dynamics
- not clear what parameter does what
- traditional approach: vary parameters, but for more than 2 D, how do you even visualize this? also slow. expensive to set up. 
- need something where parameter variation can be linked to dynamics, easy to set up, easy to use.

@@

- components from library vs. equations
- equations are transparent -- you know what you're solving. but clunky -- string parsing headaches, etc. 
- components are easy to assemble, but it;s hard to know where they are, how they can be changed, etc.
- xolotl goes the component route, but makes it very easy to find components (you can click your way into the C++ files). components are stored as source files, so you can modify it and immediately see it reflected in your model. we didn't invent another synatax for these components -- these are just C++ files.

>>>>

- failure of averaging \\
- complex interrelationships b/w parameters and dynamics\\
- not clear what parameter does what\\
- traditional approach: vary parameters, but for more than 2 D, how do you even visualize this? also slow. expensive to set up. \\
- need something where parameter variation can be linked to dynamics, easy to set up, easy to use. \\

@@

- components from library vs. equations\\
- equations are transparent -- you know what you're solving. but clunky -- string parsing headaches, etc. \\
- components are easy to assemble, but it;s hard to know where they are, how they can be changed, etc.\\
- xolotl goes the component route, but makes it very easy to find components (you can click your way into the C++ files). components are stored as source files, so you can modify it and immediately see it reflected in your model. we didn't invent another syntax for these components -- these are just C++ files. \\
